Summarize coverage

### 2015-10-26 analysis/summarize_coverage.Rmd
add .Rprofile

save_latex_coverage_table(reslong.neg %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"../paper/tables/coverage_neg.tex")
save_latex_coverage_table(reslong.pos %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"../paper/tables/coverage_pos.tex")
save_latex_coverage_table(reslong %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"../paper/tables/coverage_all.tex")

save_latex_coverage_table(reslong.neg %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"../paper/tables/coverage_neg_nopen.tex")
save_latex_coverage_table(reslong.pos %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"../paper/tables/coverage_pos_nopen.tex")
save_latex_coverage_table(reslong %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"../paper/tables/coverage_all_nopen.tex")
```

These tables show 1-the left tail instead of the left tail.
```{r}
save_latex_coverage_table(reslong.neg %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"../paper/tables/scoverage_neg.tex",switch=TRUE)
save_latex_coverage_table(reslong.pos %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"../paper/tables/scoverage_pos.tex",switch=TRUE)
save_latex_coverage_table(reslong %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"../paper/tables/scoverage_all.tex",switch=TRUE)

save_latex_coverage_table(reslong.neg %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"../paper/tables/scoverage_neg_nopen.tex",switch=TRUE)
save_latex_coverage_table(reslong.pos %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"../paper/tables/scoverage_pos_nopen.tex",switch=TRUE)
save_latex_coverage_table(reslong %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"../paper/tables/scoverage_all_nopen.tex",switch=TRUE)
```

>>>>

save_latex_coverage_table(reslong.neg %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"table/coverage_neg.tex")
save_latex_coverage_table(reslong.pos %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"table/coverage_pos.tex")
save_latex_coverage_table(reslong %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"table/coverage_all.tex")

save_latex_coverage_table(reslong.neg %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"table/coverage_neg_nopen.tex")
save_latex_coverage_table(reslong.pos %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"table/coverage_pos_nopen.tex")
save_latex_coverage_table(reslong %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"table/coverage_all_nopen.tex")
```

These tables show 1-the left tail instead of the left tail.
```{r}
save_latex_coverage_table(reslong.neg %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"table/scoverage_neg.tex",switch=TRUE)
save_latex_coverage_table(reslong.pos %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"table/scoverage_pos.tex",switch=TRUE)
save_latex_coverage_table(reslong %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n","ash.u","ash.hu"),"table/scoverage_all.tex",switch=TRUE)

save_latex_coverage_table(reslong.neg %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"table/scoverage_neg_nopen.tex",switch=TRUE)
save_latex_coverage_table(reslong.pos %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"table/scoverage_pos_nopen.tex",switch=TRUE)
save_latex_coverage_table(reslong %>% group_by(scenario,method) %>% summarize(lt = mean(value<coverthresh)),c("ash.n.s","ash.u.s","ash.hu.s"),"table/scoverage_all_nopen.tex",switch=TRUE)
```
